Supplement for: Carbon cycling in mature and regrowth forests globally: a macroecological synthesis based on the global Forest Carbon (ForC) database

### 2021-01-19 manuscript/ERL_global_C_review.Rmd
presentation of age trend figures in manuscript

Both C stocks and fluxes commonly increased significantly with stand age (Tables 1, S2, Figs. `r flux_age_trends`- `r stock_age_trends`, `r TrB_age_trends`-`r BoN_age_trends`, `r all_age_trends`; detailed below).

*ForC* contained 16 C flux variables with sufficient data for analyses of age trends in young forests (see Methods) (Figs. `r flux_age_trends`, `r all_flux_age_trends`).
Of these, ten increased significantly with $log10[age]$: $NEP$, $GPP$, $ANPP$, $ANPP_{woody}$, $ANPP_{foliage}$, $ANPP_{litterfal}$, $BNPP$, $BNPP_{fine}$, $R_{eco}$, and $R_{root}$.
The remaining six--$NPP$, $ANPP_{stem}$, $ANPP_{branch}$, $BNPP_{coarse}$, $R_{soil-het}$, and $R_{soil-het}$-–displayed no significant relationship to stand age.

"Closure" and internal consistency of the C flux budget was less successful for young than mature forests (Figs. `r TrB_age_trends`-`r BoN_age_trends`).
Summed regression equations for $R_{soil-het}$ and $R_{root}$ were generally very close to $R_{soil}$.
We calculated $R_{auto-ag}$ as the difference between $R_{eco}$ and $R_{soil}$ (except for tropical forests, which had insufficient $R_{eco}$ data), effectively guaranteeing near-closure of the CO~2~ efflux (respiration) portion of the budget (negative values in Figs. `r TrB_age_trends`-`r BoN_age_trends`).
In contrast, the  CO~2~ influx portion of the budget generally did not "close": the sum of $R_{auto}$ ($R_{root}+R_{auto-ag}$, as described above) and components of $NPP$ consistently fell short of $GPP$ by **##-##** Mg C ha^-1^ yr^-1^ , particularly in in young stands.
Moreover, there was not consistent budget closure among the components of $NPP$, and substantially different age trends resulting from the sum of components versus total $NPP$ (Figs. `r TrB_age_trends`-`r BoN_age_trends`).

@@

  knitr::include_graphics("tables_figures/stacked_age_trends/Boreal conifer_age_trends.png")
```

>>>>

C fluxes commonly increased significantly with stand age (Tables 1, S2, Figs. `r flux_age_trends`, `r TrB_age_trends`-`r BoN_age_trends`, `r all_age_trends`).
*ForC* contained 16 C flux variables with sufficient data for analyses of age trends in young forests (see Methods).
Of these, ten increased significantly with $log10[age]$: $NEP$, $GPP$, $ANPP$, $ANPP_{woody}$, $ANPP_{foliage}$, $ANPP_{litterfal}$, $BNPP$, $BNPP_{fine}$, $R_{eco}$, and $R_{root}$.
The remaining six--$NPP$, $ANPP_{stem}$, $ANPP_{branch}$, $BNPP_{coarse}$, **$R_{soil-het}$, and $R_{soil-het}$**-–displayed no significant relationship to stand age.

@@

  knitr::include_graphics("tables_figures/stacked_age_trends/Boreal conifer_age_trends.png")
```
*(paragraph on young vs mature)*

"Closure" and internal consistency of the C flux budget was less successful for young than mature forests (Figs. `r TrB_age_trends`-`r BoN_age_trends`).
Summed regression equations for $R_{soil-het}$ and $R_{root}$ were generally very close to $R_{soil}$.
We calculated $R_{auto-ag}$ as the difference between $R_{eco}$ and $R_{soil}$ (except for tropical forests, which had insufficient $R_{eco}$ data), effectively guaranteeing near-closure of the CO~2~ efflux (respiration) portion of the budget (negative values in Figs. `r TrB_age_trends`-`r BoN_age_trends`).
In contrast, the  CO~2~ influx portion of the budget generally did not "close": the sum of $R_{auto}$ ($R_{root}+R_{auto-ag}$, as described above) and components of $NPP$ consistently fell short of $GPP$, particularly in in young stands (range across forest types and ages: 0.9-7.6 Mg C ha^-1^ yr^-1^).
Moreover, there was not consistent budget closure among the components of $NPP$, and substantially different age trends resulting from the sum of components versus total $NPP$ (Figs. `r TrB_age_trends`-`r BoN_age_trends`).

*(paragraph on young vs mature)*
